Gender, race, and gun policy during the 2020 US Presidential Election: Biden more favorable among women, Black, Asian, Hispanic, Middle Eastern, and non-gun owners

### 2024-03-16 paper/paper.qmd
Remove unused file

```{r}
#| echo: false
#| message: false
#| label: tmp-label1
#| tbl-cap: tmp-caption1
# Code adapted from https://tellingstorieswithdata.com/13-ijaglm.html#logistic-regression
ces2020 |>
  ggplot(aes(x = race, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Race",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_x_discrete(limits = rev) +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

@@

```{r}
#| echo: false
#| message: false
#| label: tmp-label2
#| tbl-cap: tmp-caption2
# Code adapted from https://tellingstorieswithdata.com/13-ijaglm.html#logistic-regression
ces2020 |>
  ggplot(aes(x = gun_ownership, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Gun Ownership",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_x_discrete(limits = rev, labels = label_wrap(10)) +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

@@

We can see that Black individuals show a much stronger support for Biden as the coefficient for `raceBlack` is 2.464. Asian, Hispanic, and Middle Eastern individuals all show an increase in support for Biden with coefficients of 0.790, 0.548, and 0.288 respectively. Native Americans show a decrease in support for Biden with a coefficient of -0.536 while individuals of two or more races show neither an increase nor decrease in support for Biden with a coefficient of -0.008.

>>>>

```{r}
#| echo: false
#| message: false
#| label: fig-race-gender
#| fig-cap: Support for Trump or Biden based on gender and race
# Code adapted from https://tellingstorieswithdata.com/13-ijaglm.html#logistic-regression
ces2020 |>
  ggplot(aes(x = race, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Race",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_x_discrete(limits = rev) +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

@@

```{r}
#| echo: false
#| message: false
#| label: fig-gun-ownership-gender
#| fig-cap: Support for Trump or Biden based on gender and gun ownership
# Code adapted from https://tellingstorieswithdata.com/13-ijaglm.html#logistic-regression
ces2020 |>
  ggplot(aes(x = gun_ownership, fill = voted_for)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  labs(
    x = "Gun Ownership",
    y = "Number of respondents",
    fill = "Voted for"
  ) +
  coord_flip() +
  scale_x_discrete(limits = rev, labels = label_wrap(10)) +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

@@

We can see that Black individuals show a much stronger support for Biden as the coefficient for `raceBlack` is 2.464. Asian, Hispanic, and Middle Eastern individuals all show an increase in support for Biden with coefficients of 0.790, 0.548, and 0.288 respectively. Native Americans and Other show a decrease in support for Biden with a coefficient of -0.536 and -0.333 respectively while individuals of two or more races show neither an increase nor decrease in support for Biden with a coefficient of -0.008.
